Data driven measure of convergence for word embeddings

### 2017-07-02 draft2.tex
Notes following joint brainstorming session

>>>>

\section{Notes}
\begin{itemize}
\item Add a clarification (definition) of what it means for two spaces to be equivalent:
  \begin{itemize}
  \item Relations in one space are preserved in the other
  \item It is basically just a rotation
  \end{itemize}

 \item "Known issues:" restructure (maybe into one thing)

 \item  Pseudocode 
 \begin{itemize}
  \item Add picture (how would it look like)
  \item Add intuitive / concrete example (using a word)
 \end{itemize}

 \item Separate repo for the code

 \item Move "We use D(A,B)..." to Method section (together with clarification of definition above)
 \item Add: we used CBOW (or skip gram)

 \item Figure 2 
 \begin{itemize}
  \item density plot
  \item xaxis should be No. sentences
 \end{itemize}

 \item Figure 3
  \begin{itemize}
  \item add axis No. sentences
  \item add discussion "why is google score low"
 \end{itemize}

 \item Add in introduction why we do this more strongly

 \item Venues:
 \begin{itemize}
  \item LREC
  \item IEEE
  \item NIPS
  \item PR ?
  \item http://cs.rochester.edu/~omidb/nlpcalendar/
 \end{itemize}

\end{itemize}
